---
title: "p8105_hw6_xz2788"
author: "Xiaoyue Zhang"
date: "11/17/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First load necessary packages

```{r}
library(tidyverse)
library(leaps)
library(modelr)
```

## Problem 1

Read in the raw data of homicides and parse columns

```{r read_data, message=FALSE, warning=FALSE}
homicide = read_csv(file = "./data/homicide-data.csv",
                    col_types = "cccccdcccddc")
```

### Tidy data

Create a city_state variable and a binary variable indicating whether the homicide is solved and tidy the dataset as required

```{r tidy_data}
homicide_tidy = homicide %>% 
  mutate(city_state = str_c(city, ",", state)) %>% 
  mutate(result = ifelse(disposition == "Closed by arrest", "solved", "unsolved")) %>% 
  filter(city_state != "Dallas,TX" & city_state != "Phoenix,AZ" & city_state != "Kansas City,MO" & city_state != "Tulsa,AL") %>% 
  mutate(victim_race = ifelse(victim_race == "White", "white", "non-white")) %>% 
  mutate(victim_race = as_factor(victim_race))

#relevel "race" factor, "white" as reference
homicide_tidy$victim_race = relevel(homicide_tidy$victim_race, ref = "white")
```

### Analysis in Baltimore

Fit a logistic regression model for Baltimore

```{r logistic_model}
#"unsolved" as reference group
homicide_tidy$result = relevel(as_factor(homicide_tidy$result), ref = "unsolved")
logi_balti = homicide_tidy %>% 
  filter(city_state == "Baltimore,MD") %>% 
  glm(result ~ victim_age + victim_sex + victim_race, data = ., family = "binomial") 
logi_balti %>%  broom::tidy()
```

Obtain the estimate and CI of OR

```{r extract_OR}
conf_inter = logi_balti %>% 
  broom::confint_tidy() %>% 
  mutate(conf.low = exp(conf.low), conf.high = exp(conf.high))
logi_balti %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>% 
  select(term, OR, log_OR = estimate, p.value) %>% 
  cbind(., conf_inter) %>% 
  knitr::kable(digits = 3)
```

From the results, we can see that in Baltimore, for non-white victims, the odds of solving homicides and unsolved ones is 0.44 times the odds of that of white victims with adjusting for age and sex, which also means that homicides of white victims were more likely to be solved.

### Build logistic regression for each of the city

First creat a function to extract OR and 95%CI

```{r creat_function}
odds_confi = function(x){
  
  ci = broom::confint_tidy(x) %>% 
    mutate(conf.low = exp(conf.low), conf.high = exp(conf.high))
  or_ci = x %>% 
    broom::tidy() %>% 
    mutate(OR = exp(estimate)) %>% 
  select(term, OR, log_OR = estimate) %>% 
  cbind(., ci)
  
  return(or_ci)
  
}

```

Conduct glm in each city and delete "Unknown" victim sex for later modeling

```{r logit_city}
each_city = homicide_tidy %>% 
  filter(victim_sex != "Unknown") %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(model = map(data, ~glm(result ~ victim_age + victim_sex + victim_race, data = .x, family = "binomial"))) %>% 
  mutate(model = map(model, odds_confi)) %>% 
  select(-data) %>% 
  unnest()
head(each_city)
```

Make a plot to show ORs and CIs for each city

```{r plot_each_city}
each_city %>% 
  filter(term == "victim_racenon-white") %>% 
  transform(city_state = reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    title = "Estimated odds ratio and 95% CI of race",
    x = "City",
    y = "Estimated odds ratio of race",
    caption = "Data from the Washington Post"
  ) +
  theme(legend.position = "bottom")
```

Comment: Across the cities, Boston has the lowest estimated odds ratio for solving homicides comparing non-white victims to white victims and Tampa, FL has the highes estimated odds ratio. Only Durham and Tampa have estimated odds ratio over 1 which means in these cities, homicides of non-white victims are more likely to be solved while all other cities were the opposite, but the confidence interval included 1 which meas actually no difference between the odds ration in non-white and white victims.

## Problem 2

Read in the data first

```{r import_data}
birthweight = read_csv(file = "./data/birthweight.csv.csv")
```

Look at the data first and check NAs

```{r look_data}
str(birthweight)
skimr::skim(birthweight)
```

From the result, we can see that there is no missing value in all variables, but the classes of some variables should to be tidied.

### Tidy data

```{r clean_data}
birthweight = birthweight %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace))
```

### Modeling process

* First check whether the birthweight is normally distributed

```{r check_normality}
birthweight %>% 
  ggplot(aes(x = bwt)) + 
  geom_histogram() +
  theme_bw() +
  labs(
    title = "Birthweight distribution",
    x = "Birthweight (grams)",
    y = "Count",
    caption = "Data from 'Birthweight' dataset")
```

From the plot, birthweight seems to be normally distributed with a little bit skewness to the left tail.

* Select variables into the model by stepwise method with 'leap' function

```{r stepwise}
regsubsets(bwt~., data = birthweight, nvmax = 5, method = "seqrep") %>% 
  summary()
```

From the result, we can see that "bhead", "blength", "mrace", "delwt", "gaweeks", "smoken" can be selected into the model, but from knowledge of medicine, "malform", "wtgain", "pnumlbw" and "pnumsga" can also be related to the birthweight of the baby, but because all the data for "pnumsga" and "pnumlbw" is `r mean(birthweight$pnumlbw)`, thus they can be removed from the model

* Decide whether add "malform" and "wtgain" into the model

```{r try_models}
lm(bwt~bhead + blength + mrace + delwt + gaweeks + smoken, data = birthweight) %>% 
  summary()
lm(bwt~bhead + blength + mrace + delwt + gaweeks + smoken +
     malform + wtgain, data = birthweight) %>% 
  summary()
```

"malform" seems not to have an effect on birthweigt since the p-value of it is greater than 0.05.

* Compare models with/without "wtgain" 

```{r anova_compare}
model_1 = lm(bwt~bhead + blength + mrace + gaweeks + smoken + delwt, data = birthweight)
model_2 = lm(bwt~bhead + blength + mrace + gaweeks + smoken + delwt + wtgain, data = birthweight)
anova(model_1, model_2)
summary(model_1)
summary(model_2)
```

Although adding "wtgain" can increase the adjusted R-square, but the magnitude is not big, thus I choose to not include "wtgain". 

* Double check the collinearity among selected variables

```{r collinearity_check}
birthweight %>% 
  select(bwt, bhead, blength, delwt, gaweeks, smoken) %>% 
  cor()
```

* Final regression model:

```{r final_model}
birth_model = lm(bwt~bhead + blength + mrace + gaweeks + delwt + smoken, data = birthweight)
```

### Make a plot to show residuals against fitted values

```{r plot_regression}
birthweight %>% 
  modelr::add_predictions(birth_model) %>% 
  modelr::add_residuals(birth_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = .5) +
  theme_bw() +
  labs(
    title = "Residual VS. fitted values plot",
    x = "Predited birthweight (grams)",
    y = "Residuals",
    caption = "Data from 'Birthweight' dataset")
plot(birth_model, 1)
```

From the plot, we can see that when the birthweight is between a range of 2000 to 4000 grams which is also the standard birthweight of neonates, the final model can predicted the birthweight more accurately with less residuals. However, when birthweight is too small or too large, the residuals are too big to predict it accuarately.

### Compare with two other models

* Build other two models

```{r build_two_models}
two_pred_model = lm(bwt ~ blength + gaweeks, data = birthweight)
intera_model = lm(bwt ~ (bhead + blength + babysex)^2 +
                    (bhead + blength + babysex)^3, data = birthweight)
```

* Conduct cross validation

```{r split_data}
crossv_mc(birthweight, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(final_model = map(train, ~lm(bwt ~ bhead + blength + mrace + gaweeks + delwt + smoken, data = .x)),
         two_pred_model = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         intera_model = map(train, ~lm(bwt ~ (bhead + blength + babysex)^2 +
                    (bhead + blength + babysex)^3, data = .x))) %>% 
   mutate(rmse_final  = map2_dbl(final_model, test, ~rmse(model = .x, data = .y)),
         rmse_two_pre = map2_dbl(two_pred_model, test, ~rmse(model = .x, data = .y)),
         rmse_intera = map2_dbl(intera_model, test, ~rmse(model = .x, data = .y))) %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  theme_bw()
```

Comment: 
